% !TEX root = ../main.tex
\begin{abstract}

Optimistic rollups are in wide use today as an opt-in scalability layer for blockchains like Ethereum. In such systems, Ethereum is referred to as L1 (Layer 1) and the rollup provides an environment called L2, which reduces fees and latency but cannot instantly and trustlessly interact with L1. One practical issue for optimistic rollups is that trustless transfers of tokens and ETH, as well as general messaging, from L2 to L1 is not finalized on L1 until the passing of a dispute period (aka withdrawal window) which is currently 7 days in the two leading optimistic rollups: \arb and \opt. In this paper, we explore methods for sidestepping the dispute period when withdrawing ETH from L2 (called an exit), even in the case when it is not possible to directly validate L2. We fork the most-used rollup, \arb \nitro, to enable exits to be traded on L1 before they are finalized. We also study the combination of tradeable exits and prediction markets to enable insurance for withdraws that do not finalize. As a result, anyone (including contracts) on L1 can safely accept withdrawn tokens while the dispute period is open despite having no knowledge of what is happening on L2. Our scheme also allows users to opt-into a fast withdrawal at any time. All fees are set by open market operations.

%All fees in the arrangement---Alice pays a fee to withdraw fast, Bob is paid a fee for accepting unfinalized tokens, and Carol is awarded a fee for validating L2 and insuring the finality of the withdrawal---are set by open market operations.

% Define "fast" 

\end{abstract}